Kindly Bent to Free Us

### 2020-06-02 kindly/soa.tex
Improve the comparison matrix.

    \begin{tabular}{l|cccccccc}
      Language
      & URAL & \rot{Borrows} & \rot{State}
      & \rot{R. Subsumption}
      & \rot{R. Polymorphism}
      & \rot{Inference} & \rot{Formalisation}
      & \rot{Basis}
      \\\hline
      System F\degree~\citep{DBLP:conf/tldi/MazurakZZ10}
      & UL & --- & \N & \N & \N & \N & \YC Coq & System F
      \\
      Alms~\citep{DBLP:conf/popl/TovP11}
      & UA & \N & \Y & \M & \Y & \NC Local & \N & ML \\
      Quill~\citep{DBLP:conf/icfp/Morris16}
      & UL & --- & \N & \N & \Y & \YC Principal & \MC Manual & Qualified types\\
      Linear Haskell~\citep{DBLP:journals/pacmpl/BernardyBNJS18}
      & UL & --- & \M & \N & \Y & \MC Non-principal & \MC Manual & Haskell \\
      Rust~\citep{rust}
      & UA & \Y & \Y & \Y & \M & \NC Local & \YC Coq & ---
      \\\hline
      \lang
      & UAL & \Y & \Y & \Y & \Y & \YC Principal & \MC Manual & ML/HM(X)
      \\
    \end{tabular}
  \end{center}
  \caption{Comparison matrix}
  \label{fig:comparison-matrix}
\end{figure}

@@

The comparison matrix in \cref{fig:comparison-matrix} gives an
overview over the systems discussed in this section. The column URAL
specifies the substructural features. Borrows and state are
self-explanatory. Subsumption indicates that kind U is promoted
to A and further to L. Polymorphism refers to polymorphism over
substructural kinds. Inference is self-explanatory, formalisation
refers to the formal semantics and type soundness proof. Basis is self-explanatory.

>>>>

    \begin{tabular}{l|ccccccccc}
      \textbf{Language}
      & URAL & \rot{Borrows} & \rot{State}
      & \rot{R. Subsumption}
      & \rot{R. Polymorphism}
      & \rot{Identity}
      & \rot{Inference} & \rot{Formalisation}
      & \rot{Basis}
      \\\hline
      System F\degree~\citep{DBLP:conf/tldi/MazurakZZ10}
      & UL & --- & \N & \N & \N & \N & \N & \YC Coq & System F
      \\
      Alms~\citep{DBLP:conf/popl/TovP11}
      & UA & --- & \Y & \M & \Y & \Y & \MC Local & \N & ML \\
      Quill~\citep{DBLP:conf/icfp/Morris16}
      & UL & --- & \N & \N & \Y & \N & \YC Principal & \MC Manual & Qualified types\\
      Lin. Haskell~\citep{DBLP:journals/pacmpl/BernardyBNJS18}
      & UL & --- & \M & \N & \Y & \N & \MC Non-principal & \MC Manual & Haskell \\
      Mezzo~\citep{DBLP:phd/hal/Protzenko14}
      & UAL & --- & \Y & \M & \Y & \Y & \N & \MC Manual & --- \\
      \hline
      Rust~\citep{rust}
      & UA & \Y & \Y & \Y & \M & \N & \MC Local & \YC Coq & --- \\
      Plaid~\citep{DBLP:conf/oopsla/AldrichSSS09}
      & UA & --- & \Y & \Y & \Y & \Y & \N & \MC Manual & --- \\
      \hline
      \lang
      & UAL & \Y & \Y & \Y & \Y & \N & \YC Principal & \MC Manual & ML/HM(X)
      \\
    \end{tabular}
  \end{center}
  \caption{Comparison matrix}
  \label{fig:comparison-matrix}
\end{figure}

@@

The comparison matrix in \cref{fig:comparison-matrix} gives an
overview over the systems discussed in this section. The column UAL
specifies the substructural features. Borrows and state are
self-explanatory. ``Subsumption'' indicates that unrestricted elements
can be promoted to affine and then linear. This applies to resources,
borrows, or closures. ``Polymorphism'' refers to polymorphism over
usage (unrestricted, affine, linear), notably for closures.
``Identity'' indicates that the language supports a notion
of identity, usually through existential types, as described in
\cref{identity}.
Inference is self-explanatory, formalisation
refers to the formal semantics and type soundness proof. Basis is self-explanatory.
